Learning how to act: making good decisions with machine learning

### 2017-10-14 thesis/talk/do_calculus_examples.tex

\definecolor{talk}{HTML}{729FCF}
\definecolor{talk2}{HTML}{E8A753}
\definecolor{grey}{HTML}{DBDCDD}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\tikzset{
    %Define standard arrow tip
    >=stealth',
    %Define style for boxes
    observed/.style={
   	circle,
   	rounded corners,
   	draw=black, thick,
   	minimum width=2.3em,
   	minimum height=2.3em,
   	font=\footnotesize,
   	text centered,
   	fill=talk!50
   },
   latent/.style={
   	circle,
   	rounded corners,
   	draw=black, thick, dashed,
   	minimum width=2.2em,
   	minimum height=2.2em,
   	font=\footnotesize,
   	text centered
   },
    % Define arrow style
    pil/.style={
           o->,
           thick,
           shorten <=2pt,
           shorten >=2pt,},
    sh/.style={ shade, shading=axis, left color=red, right color=green,
    shading angle=45 },
observedrect/.style={
	rectangle,
	rounded corners,
	draw=black, thick,
	minimum width=3em,
	minimum height=1.5em,
	font=\footnotesize,
	text centered,
	fill=talk2!80
},  
 target/.style={
	circle,
	rounded corners,
	draw=black, thick,
	minimum width=2.3em,
	minimum height=2.3em,
	font=\footnotesize,
	text centered,
	fill=talk2!80
},
empty/.style={
	circle,
	rounded corners,
	minimum width=.5em,
	minimum height=.5em,
	font=\footnotesize,
	text centered,
},
}

>>>>

\definecolor{talk}{HTML}{729FCF}
\definecolor{talk2}{HTML}{E8A753}
\definecolor{grey}{HTML}{DBDCDD}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\tikzset{
    %Define standard arrow tip
    >=stealth',
    %Define style for boxes
    observed/.style={
   	circle,
   	rounded corners,
   	draw=black, thick,
   	minimum width=2.3em,
   	minimum height=2.3em,
   	font=\footnotesize,
   	text centered,
   	fill=talk!50
   },
   latent/.style={
   	circle,
   	rounded corners,
   	draw=black, thick, dashed,
   	minimum width=2.2em,
   	minimum height=2.2em,
   	font=\footnotesize,
   	text centered
   },
    % Define arrow style
    pil/.style={
           o->,
           thick,
           shorten <=2pt,
           shorten >=2pt,},
    sh/.style={ shade, shading=axis, left color=red, right color=green,
    shading angle=45 },
observedrect/.style={
	rectangle,
	rounded corners,
	draw=black, thick,
	minimum width=3em,
	minimum height=1.5em,
	font=\footnotesize,
	text centered,
	fill=talk!50
},  
 target/.style={
	circle,
	rounded corners,
	draw=black, thick,
	minimum width=2.3em,
	minimum height=2.3em,
	font=\footnotesize,
	text centered,
	fill=talk!50
},
empty/.style={
	circle,
	rounded corners,
	minimum width=.5em,
	minimum height=.5em,
	font=\footnotesize,
	text centered,
},
}

### 2017-10-14 thesis/talk/unfaithful_chocolate_obesity.tex

\begin{enumerate}
\item D-separation still applies after intervention.

${(Cancer \ci Asthma|Smoke)_{G_{\overline{X}}} \implies P(Cancer|do(Smoke),Asthma) = P(Cancer|do(Smoke)}$
\item If there are no backdoor paths from $X$ to $Y$ then intervention$\equiv$observation.

${(\hat{X} \ci Cancer|X,Poverty)_{G^{\dagger}} \implies P(Cancer|do(Smoke),Poverty) = P(Cancer|Smoke,Poverty)}$
\item If there are only backdoor paths from $X$ to $Y$ then intervention doesn't change $P(Y)$.

$(\hat{X} \ci Diet)_{G^{\dagger}} \implies P(Diet|do(Smoke)) = P(Diet)$
\end{enumerate}
\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\caption{$G^{\dagger}$}
\begin{tikzpicture}[->,shorten >=0pt,shorten <=0pt,node distance=0.45cm,thick,main node/.style={observed}]
\node[main node](X){X=Smoke};
\node[main node, above right=of X](P){Poverty};
\node[main node, below right=of P](D){Diet};
\node[main node, below right=of X](C){Cancer};
\node[main node, fill=red!20!yellow, above left=of X](Switch){$\hat{X}$};
\node[main node, below left=of X](A){Asthma};
\path[]
	(Switch) edge (X)
	(X) edge (C)
	(D) edge (C)
	(X) edge (A)
	(P) edge (D) edge (X);
\end{tikzpicture}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\caption{$G_{\overline{X}}$}
\begin{tikzpicture}[->,shorten >=0pt,shorten <=0pt,node distance=0.45cm,  thick,main node/.style={observed}, shaded/.style={latent}]
\node[main node](X){X=Smoke};
\node[main node, above right=of X](P){Poverty};
\node[main node, below right=of P](D){Diet};
\node[main node, below right=of X](C){Cancer};
\node[main node, below left=of X](A){Asthma};
\path[]
	(X) edge (C) edge (A)
	(D) edge (C)
	(P) edge (D);
\end{tikzpicture}
\end{subfigure}
\end{figure}

>>>>

%\multicolumn{'num_cols'}{'alignment'}{'contents'}

\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.6\textwidth}
\centering
\caption{True causal graph generating $P$}
\begin{tikzpicture}[->,shorten >=0pt,shorten <=0pt,node distance=0.45cm,thick,main node/.style={observed}]
\node[main node, align=center,minimum height=4.3em](C){\textbf{Chocolate} \\ \begin{tabular}{| c | c | c |}
  \hline			
  Income & H & L \\
  \hline
  P(C=H) & .8639 & .2\\
  \hline
\end{tabular}};
\node[main node, above right=of C, align=center](I){\textbf{Income} \\ $P(I=High) = 0.5$};
\node[main node, below right=of I, align=center,minimum height=4.3em](O){\textbf{Obesity} \\ \begin{tabular}{| c | c | c | c | c |}
  \hline			
  Income & \multicolumn{2}{| c |}{H} & \multicolumn{2}{| c |}{L} \\
  \hline
  Chocolate & H & L & H & L \\
  \hline
  $P(O=Y)$ & .4 & .2 & .7 & .5 \\
  \hline
\end{tabular}};
\path[]
	(I) edge (C) edge (O)
	(C) edge (O);
\end{tikzpicture}
\end{subfigure}
\begin{subfigure}[t]{0.3\textwidth}
\centering
\caption{Perfect map for $P, \;(C \ci O)$}
\begin{tikzpicture}[->,shorten >=0pt,shorten <=0pt,node distance=0.45cm,  thick,main node/.style={observed}, shaded/.style={latent}]
\node[main node](C){Chocolate};
\node[main node, below right=of C](I){Income};
\node[main node, above right=of I](O){Obesity};
\path[]
	(C) edge (I)
	(O) edge (I);
\end{tikzpicture}
\end{subfigure}
\end{figure}
